---
title: "Code Book"
author: "Kit Smith"
date: "7/1/2020"
output: rmarkdown::github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
This code book describes how the data in the ```UCI HAR Dataset``` was transformed into ```tidydata.txt``` and summarizes the variables thereof. 

****** 

### Data

```tidydata.txt``` contains data from the following files the ```UCI HAR Dataset``` :

    •	"features.txt"

    •	"activity_labels.txt"

    •	"train/X_train.txt"

    •	"train/y_train.txt"

    •	"test/X_test.txt"

    •	"test/y_test.txt"

****** 

### Transformation


The R script, ```run_analysis.R```, does the following:

1. Downloads and unzips the dataset
    
2. Loads the relevant files
    
3. Extracts the mean and standard deviation columns from the training and test datasets
    
4. Merges the data and adds descriptive activity names

5. Creates a tidy dataset showing the mean value of each variable by subject

6. Stores the above data set in the file ```tidydata.txt```
    

The script uses both the ```dplyr``` and ```mgsub``` packages.

******

### Variables

##### Identifiers
```subject``` - the test subject  
```activity``` - the activity performed  <cr>

##### Activity Labels
```{r,echo = FALSE, comment=NA}
    df<-data.frame(values = c(1:6), activity = c("WALKING", "WALKING_UPSTAIRS", "WALKING_DOWNSTAIRS", "SITTING", "STANDING", "LAYING"))
print(df, row.names = FALSE)
```
##### Mesurements
```{r,echo = FALSE, comment=NA}
features <- read.table("UCI HAR Dataset/features.txt")
means <- grep("mean()|std()", features[,2])

df2<-data.frame(Measurment = sapply(features[,2], function(x) {gsub("[()]","",x)})[means])
print(df2, row.names= FALSE, col.names = FALSE)

```
